---
title: "Forum SNA - Masters of HRM"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 6,
                      fig.height = 6)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggraph))
suppressPackageStartupMessages(library(tidygraph))
library(bb.fm.tools)
```

``` {r load_data}
fm_all <- read_csv(file.path('~', 'Data', 'ad hoc', 'fm masters of HRM 201960 90 201930.csv')) 

# fm_all <- fm_all %>% 
#     mutate(msg_text = map_chr(msg_text, XML::htmlParse))
# 
# SA <- SentimentAnalysis::analyzeSentiment(fm_all$msg_text, language = "english")

fm_nest <- fm_all %>% 
    group_by(subject) %>% 
    nest() %>% 
    mutate(graph = map(data, fm_graph)) 

fm_nest <- fm_nest %>% 
    mutate(plot_basic = 
               map2(.x = graph, 
                    .y = subject,
                    .f = ~fm_plot(.x, 
                                  title = paste("Forum network for", .y),
                                  remove_isolates = TRUE)
               )) 

fm_nest <- fm_nest %>% 
    mutate(session = as.numeric(str_sub(subject, 10, 15))) %>% 
    arrange(session, subject)

```

# Forum Networks

Nodes represent people and are coloured by their role in the course.

Edges represent an aggregate of all posts and replies between those two people. Darker lines included posts that were read more (by anyone in the course) and lighter lines were read less. Redder lines represent a collection of posts later in the course and bluer lines represent a collection of posts earlier in the course. 

``` {r}
fm_nest$plot_basic
```
